\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{natbib}
\usepackage{graphicx}

\newcommand{\emailaddr}[1]{\href{mailto:#1}{\texttt{#1}}}

\title{\LARGE
    PPS Final Report
}

\author{
    Davide Evangelisti \\ \emailaddr{davide.evangelisti2@studio.unibo.it}
    \and 
    Francesco Dente \\ \emailaddr{francesco.dente@studio.unibo.it} 
    \and 
    Shapour Nemati \\ \emailaddr{shapour.nemati@studio.unibo.it}
    \and 
    Simone Magnani \\ \emailaddr{simone.magnani4@studio.unibo.it} 
    
}

\date{\today}

\begin{document}

\maketitle

Ricordatevi che la lettura della relazione fino a: (i) i requirement, deve essere sufficiente per uno sviluppatore per giungere ad un sistema che fa quello che fa il vostro; (ii) al design, deve essere sufficiente per uno sviluppatore per giungere ad un sistema che in più è organizzato come il vostro; (iii) alla implementazione, è essenzialmente equivalente al vostro.

\begin{abstract}
    Up to $\sim$2000 characters briefly describing the project.
    
    Non si faccia mancare all'inizio una descrizione anche sommaria di cosa il sistema implementato realizza.
Vista la mole di lavoro dietro al progetto, difficile pensare che i requirement occupino meno di 2-3 facciate: siano più sistematici possibili


Forse non deve essere un abstract?
\end{abstract}

\input{tex/processo_di_sviluppo}

\input{tex/requisiti}

\input{tex/design_architetturale}

\input{tex/design_di_dettaglio}

\input{tex/implementazione}

\input{tex/retrospettiva}

\section*{Stylistic Notes}

Use a uniform style, especially when writing formal stuff: $X$, X, $\mathbf{X}$, $\mathcal{X}$, \texttt{X} are all different symbols possibly referring to different entities. 

This is a very short paragraph.

This is a longer paragraph (notice the blank line in the code).
It composed by several sentences.
%
You're invited to use comments within \texttt{.tex} source files to separate sentences composing the same paragraph.

Paragraph should be logically atomic: a subordinate sentence from one paragraph should always refer to another sentence from within the same paragraph.

The first line of a paragraph is usually indented.
%
This is intended: it is the way \LaTeX{} lets the reader know a new paragraph is beginning.

Use the \href{https://en.wikibooks.org/wiki/LaTeX/Source_Code_Listings}{\texttt{listing}} package for inserting scripts into the \LaTeX{} source.

\nocite{*} % Includes all references from the `references.bib` file
\bibliographystyle{plain}
\bibliography{references}

\end{document}
